Python as a machine learning language: experiences from the scikit-learn project

### 2013-06-14 paper.tex
remove Bertrand, move Gael as last author

\author{Lars Buitinck~\inst{1,2} \and
        Gilles Louppe~\inst{1,2} \and
        Mathieu Blondel~\inst{1,2} \and
        Fabian Pedregosa~\inst{2} \and
        Andreas Mueller~\inst{2} \and
        Gaël Varoquaux~\inst{2} \and
        Olivier Grisel~\inst{2} \and
        Vlad Niculae~\inst{2} \and
        Peter Prettenhofer~\inst{2} \and
        Alexandre Gramfort~\inst{2} \and
        Jacques Grobler~\inst{2} \and
        Robert Layton~\inst{2} \and
        Jake Vanderplas~\inst{2} \and
        Arnaud Joly~\inst{2} \and
        Bernard Thirion}

>>>>

\author{Lars~Buitinck~\inst{1,2} \and
        Gilles~Louppe~\inst{1,2} \and
        Mathieu~Blondel~\inst{1,2} \and
        Fabian~Pedregosa~\inst{2} \and
        Andreas~Mueller~\inst{2} \and
        Olivier~Grisel~\inst{2} \and
        Vlad~Niculae~\inst{2} \and
        Peter~Prettenhofer~\inst{2} \and
        Alexandre~Gramfort~\inst{2} \and
        Jacques~Grobler~\inst{2} \and
        Robert~Layton~\inst{2} \and
        Jake~Vanderplas~\inst{2} \and
        Arnaud~Joly~\inst{2} \and
        Gaël~Varoquaux~\inst{2}}
